### 2016-09-30 BF_correctness.tex
cleaning up section 4
cheers
added note for Jon about RO usage in the correctness game
changes to GBF and BF
cleaning bf and gbf still

%\section{Proof of Theorem~\ref{thm:bf-correctness}}
%\label{sec:thm3_fp}
\begin{proof}[Theorem~\ref{thm:bf-correctness}]
We use a game playing argument, please refer to Figures~\ref{fig:bf-correctness-games1} and~\ref{fig:bf-correctness-games2}. In $\game{0}$, the $\Hash$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO). For every distinct query, $\Hash$ returns a random value sampled from $[m]$. Here, the adversary $A$, along with $\Rep$ and $\Qry$ are given access to $\Hash$. It can be seen that, $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{Bloom}}$. So, $\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} = \Prob{\game{0}(A) = 1}$.

$\game{1}$ is exactly same as $\game{0}$ except the $\Qry$ oracle is replaced by the code of $\Qry$, whereas in $\game{2}$, the $\Test$ oracle returns the hash values back to the adversary along with output of the $\Qry$ oracle. $\game{3}$ on the other hand, returns all the $k$ hash values for any query. This results in adversary getting $(k-1)$ hash values for free as we charge the adversary for a single query. Since $k$ is likely to be very small compared to the number of queries the adversary makes, this would not affect the analysis in any significant manner. Also, in real world, RO will be a hash function; hence the adversary can perform local computations to get the hash values. It can be easily seen that the output of all the games will be same. So, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1} = \Prob{\game{2}(A) = 1} = \Prob{\game{3}(A) = 1}$.

In $\game{4}$, assuming $A$ does not make any pointless queries, $\Hash$ returns $k$ random values (for each query) sampled from $[m]$. Also, we offload all of $\Test$'s computations to $\Hash$, which now maintains an $\Ans$ table to compute and save answers for each query.  For any query, $\qry$, the $\Test$ oracle returns answer stored at $\Ans[\qry]$. We also introduce the $\bad$ flag in this game. Like in the earlier proofs,  $\bad$ is set to true, if queries indexed by the r-set $\calI$ fail to be false positives, or the other queries are false-positives. $\bad$ in fact does not affect the output of $\Hash$ or the game. So, $\Prob{\game{4}(A) = 1} = \Prob{\game{3}(A) = 1}$.

$\game{5}$ is exactly same as $\game{4}$, but returns 0, if $\bad$ is set to true. It can be observed that, the total queries made to the $\Hash$ oracle by the adversary is the sum of queries($q_T$) made by the $\Test$ oracle, and adversary's direct queries($q_H$) to the RO. Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.

For $r=1$, $\game{5}$ exactly simulates the classical Bloom filter. Since, $\Hash$ returns random values for each query, the event of getting a false-positive is independent of the index of the query. Using Kirsch and Mitzenmacher's upper bound on false positive probability of a classical Bloom filter, we have  $\Prob{\game{5}(A)=1} = \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.

@@

\underline{\game{0}(A)}\\

@@

$\bot \getsr A^{\TestOracle}(\pubaux)$\\

@@

\nudge $h_j \gets \HashOracle(j, x)$\\

@@

$(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\

@@

\caption{\ref{thm:bf-correctness}: Game playing argument}

@@

\underline{\game{4}(A)\fbox{\game{5}(A)}}\\

@@

$S \getsr A$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\

@@

if $\Ans[x] \neq \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\

@@

\caption{\ref{thm:bf-correctness}: $\game{4}$ and $\game{5}$ of game
  playing argument}

>>>>

%\section{Proof of Theorem~\ref{thm:bf-correctness}}
%\label{sec:thm3_fp}
\begin{proof}[Theorem~\ref{thm:bf-correctness}]
We use a game playing argument, please refer to Figures~\ref{fig:bf-correctness-games1} and~\ref{fig:bf-correctness-games2}. In game $\game{0}$, the $\Hash$ oracle performs lazy sampling of elements from $[m]$ to mimic a random oracle (RO). For every distinct query, $\Hash$ returns a random value sampled from $[m]$. It can be seen that, game $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{gbf}}$.  So, $\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} = \Prob{\game{0}(A) = 1}$.

Game $\game{1}$ is exactly same as game $\game{0}$ except the $\Qry$ call (inside the $\TestOracle$ oracle) is replaced by the code of $\Qry$.  Hence, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1}$.

In game $\game{2}$, the $\Test$ oracle is altered to return the hash values~$h_1,h_2,\ldots, h_k$ in addition to the result of executing the code of $\Qry$.  As this only provides additional information to the adversary, $\Prob{\game{1}(A) = 1} \leq \Prob{\game{2}(A) = 1}$.

In $\game{3}$, we modify the $\HashOracle$ oracle so that on query~$\qry_x$ it returns all of the~$k$ values that previously would have required calls $\HashOracle(1,\qry_y),\HashOracle(2,\qry_y),\ldots,\linebreak\HashOracle(k,\qry_y)$.  This results in adversary getting $(k-1)$ hash values ``for free'', as we charge the adversary only for a single query.  We alter the $\TestOracle$ oracle accordingly, so that it makes a single call $\Hash(\qry_x)$ rather than~$k$ such calls.  
We do this so that we can assume that a call~$\HashOracle(\qry_x)$ is pointless after a~$\TestOracle(\qry_x)$ call, and this will aid us in subsequent games.  \fixme{for BF proof, this actually does more, it makes a hash query as good as a test query, because~$M$ is public.}  Thus, $\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.

%tom here
Game~$\game{4}$ contains some important changes from game~$\game{3}$, but we will argue that $\Prob{\game{3}(A) = 1} \leq \Prob{\game{4}(A) = 1}$.  To begin, in game~$\game{4}$ we sample an $r$-subset of indices from~$\{1,2,\ldots,q_H+q_T\}$.  (We will see why, shortly.)  Next, the $\TestOracle$ oracle on input~$\qry_x$ no longer computes its answer directly, but instead refers to a new table~$\mathrm{Ans}[x]$ which is populated upon calls to the $\HashOracle$ oracle.  In particular, if $\mathrm{Ans}[x]$ is undefined, $\TestOracle$ makes a $\HashOracle(\qry_x)$ call; otherwise, it returns the contents of~$\mathrm{Ans}[x]$, which contains exactly the values that~$\TestOracle(\qry_x)$ would have returned in the previous game.  The $\HashOracle$ oracle, on input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in $\game{3}$.  (We no longer need to maintain the table~$T$ because hash values are only determined by~$\HashOracle$ calls, and these are never repeated under our no-pointless-query assumption.)  It then computes the answer that~$\TestOracle(\qry_x)$ would return, in game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use by~$\TestOracle$.  The $\HashOracle$ oracle also introduces a query counter~$c$, which is incremented whenever~$\HashOracle$ is called, either directly by~$A$ or via~$A$ having made a~$\TestOracle$ query on~$\qry_x$ where~$\mathrm{Ans}[x]$ had not been previously defined by a~$\HashOracle(\qry_x)$ call.  \fixme{for BF proof, we can assume that $\TestOracle(\qry_x)$ is never made after a~$\HashOracle(\qry_x)$ call, because~$M$ is public.  And vice versa.  So the maximum value of~$c = q_T + q_H$.}  (Note that the maximum value of~$c$ is $q_T + q_H$.)  The set~$\calI$ contains a set of~$r$ distinct values from $\{1,2,\ldots,q_T+q_H\}$ and, intuitively, these are the game's ``guesses'' at the $\HashOracle$ queries that will result in a correctness error.  If these~$r$ guesses are incorrect, then a boolean flag~$\bad$ is set, although in game~$\game{4}$ the value of~$\bad$ has no effect on the games execution; in particular, $\game{4}$ does \emph{not} contain the boxed ``Return 0'' statement.

Games~$\game{4}$ and $\game{5}$ are identical except for this boxed statement.  In particular, game~$\game{5}$ returns 1 exactly when~$\game{4}$ would return 1 \emph{and} the boolean~$\bad$ would have remained false in~$\game{4}$.   This implies that~$game{4}$ managed to guess exactly the queries that would result in correctness errors, and hence
$\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.

\fixme{Tom stopped his clean-up here.  Fix this last paragraph!}
For $r=1$, $\game{5}$ exactly simulates the classical Bloom filter. Since, $\Hash$ returns random values for each query, the event of getting a false-positive is independent of the index of the query. Using Kirsch and Mitzenmacher's upper bound on false positive probability of a classical Bloom filter, we have  $\Prob{\game{5}(A)=1} = \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.

@@

\underline{$\game{0}(A)$}\\

@@

$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\

@@

\nudge $h_j \gets \HashOracle(j, \qry_x)$\\

@@

$(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\

@@

\caption{Games $\game{0}$-$\game{3}$ for the
proof of Theorem~\ref{thm:bf-correctness}.}

@@

\underline{$\game{4}(A)$\fbox{$\game{5}(A)$}}\\

@@

$S \getsr A$; $\mathcal{I}\getsr [\{1,2,\ldots,q_T+q_H\}]^r$\\

@@

if $\Ans[x] = \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\

@@

\caption{Games $\game{4}$-$\game{5}$ for the
proof of Theorem~\ref{thm:bf-correctness}.}

### 2016-09-30 GBF-correctness-private-M.tex
cleaning bf and gbf still

%\section{Proof of Theorem~\ref{thm:bf-correctness}}
%\label{sec:thm3_fp}
\begin{proof}[Theorem~\ref{thm:gbf-correctness}]
We use a game playing argument, please refer to Figures~\ref{fig:gbf-correctness-games1} and~\ref{gfig:bf-correctness-games2}. In game $\game{0}$, the $\Hash$ oracle performs lazy sampling of elements from $[m]$ to mimic a random oracle (RO). For every distinct query, $\Hash$ returns a random value sampled from $[m]$. It can be seen that, game $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{gbf}}$.  So, $\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} = \Prob{\game{0}(A) = 1}$.

@@

%tom here
Game~$\game{4}$ contains some important changes from game~$\game{3}$, but we will argue that $\Prob{\game{3}(A) = 1} \leq \Prob{\game{4}(A) = 1}$.  To begin, in game~$\game{4}$ we sample an $r$-subset of indices from~$\{1,2,\ldots,q_H+q_T\}$.  (We will see why, shortly.)  Next, the $\TestOracle$ oracle on input~$\qry_x$ no longer computes its answer directly, but instead refers to a new table~$\mathrm{Ans}[x]$ which is populated upon calls to the $\HashOracle$ oracle.  In particular, if $\mathrm{Ans}[x]$ is undefined, $\TestOracle$ makes a $\HashOracle(\qry_x)$ call; otherwise, it returns the contents of~$\mathrm{Ans}[x]$, which contains exactly the values that~$\TestOracle(\qry_x)$ would have returned in the previous game.  The $\HashOracle$ oracle, on input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in $\game{3}$.  We no longer need to maintain the table~$T$ because hash values are only determined by~$\HashOracle$ calls.

In $\game{4}$, assuming $A$ does not make any pointless queries, $\Hash$ returns $k$ random values (for each query) sampled from $[m]$. Also, we offload all of $\Test$'s computations to $\Hash$, which now maintains an $\Ans$ table to compute and save answers for each query.  For any query, $\qry$, the $\Test$ oracle returns answer stored at $\Ans[\qry]$. We also introduce the $\bad$ flag in this game. Like in the earlier proofs,  $\bad$ is set to true, if queries indexed by the r-set $\calI$ fail to be false positives, or the other queries are false-positives. $\bad$ in fact does not affect the output of $\Hash$ or the game. So, $\Prob{\game{4}(A) = 1} = \Prob{\game{3}(A) = 1}$.

$\game{5}$ is exactly same as $\game{4}$, but returns 0, if $\bad$ is set to true. It can be observed that, the total queries made to the $\Hash$ oracle by the adversary is the sum of queries($q_T$) made by the $\Test$ oracle, and adversary's direct queries($q_H$) to the RO. Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.

For $r=1$, $\game{5}$ exactly simulates the classical Bloom filter. Since, $\Hash$ returns random values for each query, the event of getting a false-positive is independent of the index of the query. Using Kirsch and Mitzenmacher's upper bound on false positive probability of a classical Bloom filter, we have  $\Prob{\game{5}(A)=1} = \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.

@@

\oracle{$\HashOracle(\qry_y)$}\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
\nudge if $T[j,y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,y]$\\
\nudge $T[j,y] \gets v_j$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Games $\game{0}$-$\game{3}$ for the
proof of Theorem~\ref{thm:gbf-correctness}.}
\label{fig:gbf-correctness-games1}
\end{figure}
\begin{figure}[tp]
\fpage{.95}{
\hpagessl{.4}{.5}
{
\underline{\game{4}(A)\fbox{\game{5}(A)}}\\
$c\gets 0$, $\bad \gets \false$\\
$\err \gets 0$;  $\calC \gets \emptyset$\\
$S \getsr A$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
if $\Ans[x] = \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
Return $\Ans[x]$\\

}
{
\oracle{$\HashOracle(\qry_y)$}\\
$c \gets c + 1$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
%
$M \gets\privaux$\\
$y' \gets M[v_1] \xor M[v_2] \xor \ldots \xor M[v_k]$\\
if $y' \neq y$ then \\
\nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
\nudge if $c \in \calI$ then $\bad \gets \true$\\
\nudge Return $\left(v_1,\ldots,v_k\right)$\\
if $c \notin \calI$ then $\bad \gets \true$\\
$\err \gets \err +1$\\
$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Games $\game{4}$-$\game{5}$ for the
proof of Theorem~\ref{thm:gbf-correctness}.}
\label{fig:gbf-correctness-games2}
\end{figure}
\hfill\qed
\end{proof}

>>>>

%\section{Proof of Theorem~\ref{thm:bf-correctness}}
%\label{sec:thm3_fp}
\begin{proof}[Theorem~\ref{thm:gbf-correctness}]
We use a game playing argument, please refer to Figures~\ref{fig:gbf-correctness-games1} and~\ref{fig:gbf-correctness-games2}. In game $\game{0}$, the $\Hash$ oracle performs lazy sampling of elements from $[m]$ to mimic a random oracle (RO). For every distinct query, $\Hash$ returns a random value sampled from $[m]$. It can be seen that, game $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{gbf}}$.  So, $\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} = \Prob{\game{0}(A) = 1}$.

@@

%tom here
Game~$\game{4}$ contains some important changes from game~$\game{3}$, but we will argue that $\Prob{\game{3}(A) = 1} \leq \Prob{\game{4}(A) = 1}$.  To begin, in game~$\game{4}$ we sample an $r$-subset of indices from~$\{1,2,\ldots,q_H+q_T\}$.  (We will see why, shortly.)  Next, the $\TestOracle$ oracle on input~$\qry_x$ no longer computes its answer directly, but instead refers to a new table~$\mathrm{Ans}[x]$ which is populated upon calls to the $\HashOracle$ oracle.  In particular, if $\mathrm{Ans}[x]$ is undefined, $\TestOracle$ makes a $\HashOracle(\qry_x)$ call; otherwise, it returns the contents of~$\mathrm{Ans}[x]$, which contains exactly the values that~$\TestOracle(\qry_x)$ would have returned in the previous game.  The $\HashOracle$ oracle, on input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in $\game{3}$.  (We no longer need to maintain the table~$T$ because hash values are only determined by~$\HashOracle$ calls, and these are never repeated under our no-pointless-query assumption.)  It then computes the answer that~$\TestOracle(\qry_x)$ would return, in game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use by~$\TestOracle$.  The $\HashOracle$ oracle also introduces a query counter~$c$, which is incremented whenever~$\HashOracle$ is called, either directly by~$A$ or via~$A$ having made a~$\TestOracle$ query on~$\qry_x$ where~$\mathrm{Ans}[x]$ had not been previously defined by a~$\HashOracle(\qry_x)$ call.  \fixme{for BF proof, we can assume that $\TestOracle(\qry_x)$ is never made after a~$\HashOracle(\qry_x)$ call, because~$M$ is public.  And vice versa.  So the maximum value of~$c = q_T + q_H$.}  (Note that the maximum value of~$c$ is $q_T + q_H$.)  The set~$\calI$ contains a set of~$r$ distinct values from $\{1,2,\ldots,q_T+q_H\}$ and, intuitively, these are the game's ``guesses'' at the $\HashOracle$ queries that will result in a correctness error.  If these~$r$ guesses are incorrect, then a boolean flag~$\bad$ is set, although in game~$\game{4}$ the value of~$\bad$ has no effect on the games execution; in particular, $\game{4}$ does \emph{not} contain the boxed ``Return 0'' statement.

Games~$\game{4}$ and $\game{5}$ are identical except for this boxed statement.  In particular, game~$\game{5}$ returns 1 exactly when~$\game{4}$ would return 1 \emph{and} the boolean~$\bad$ would have remained false in~$\game{4}$.   This implies that~$game{4}$ managed to guess exactly the queries that would result in correctness errors, and hence
$\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.

@@

\oracle{$\HashOracle(\qry_y)$}\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
\nudge if $T[j,y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,y]$\\
\nudge $T[j,y] \gets v_j$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Games $\game{0}$-$\game{3}$ for the
proof of Theorem~\ref{thm:gbf-correctness}.}
\label{fig:gbf-correctness-games1}
\end{figure}
\begin{figure}[tp]
\fpage{.95}{
\hpagessl{.4}{.5}
{
\underline{$\game{4}(A)$\fbox{$\game{5}(A)$}}\\
$c\gets 0$, $\bad \gets \false$\\
$\err \gets 0$;  $\calC \gets \emptyset$\\
$S \getsr A$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
if $\Ans[x] = \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
Return $\Ans[x]$\\
}
{
\oracle{$\HashOracle(\qry_y)$}\\
$c \gets c + 1$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
%
$M \gets\privaux$\\
$y' \gets M[v_1] \xor M[v_2] \xor \ldots \xor M[v_k]$\\
if $y' \neq y$ then \\
\nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
\nudge if $c \in \calI$ then $\bad \gets \true$\\
\nudge Return $\left(v_1,\ldots,v_k\right)$\\
if $c \notin \calI$ then $\bad \gets \true$\\
$\err \gets \err +1$\\
$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
%
\fpage{.95}{
\hpagessl{.4}{.5}
{
\underline{$\game{6}(A)$}}\\
$c\gets 0$, $\bad \gets \false$\\
$\err \gets 0$;  $\calC \gets \emptyset$\\
$S \getsr A$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
if $\Ans[x] = \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
Return $\Ans[x]$\\
}
{
\oracle{$\HashOracle(\qry_y)$}\\
$c \gets c + 1$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
%
$M \gets\privaux$\\
$y' \gets M[v_1] \xor M[v_2] \xor \ldots \xor M[v_k]$\\
if $y' \neq y$ then \\
\nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
\nudge if $c \in \calI$ then $\bad \gets \true$\\
\nudge Return $\left(v_1,\ldots,v_k\right)$\\
if $c \notin \calI$ then $\bad \gets \true$\\
$\err \gets \err +1$\\
$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Games $\game{4}$-$\game{5}$ for the
proof of Theorem~\ref{thm:gbf-correctness}.}
\label{fig:gbf-correctness-games2}
\end{figure}
\hfill\qed
\end{proof}
